DeepPicar:​ ​A​ ​Low-cost​ ​Deep​ ​Neural​ ​Network-based​ ​Autonomous​ ​Car

### 2017-10-04 paper/evaluation.tex
revision evaluation c. multimodel:

We also test the capability of the DeepPicar to run multiple models at
the same time, and whether each model can successfully perform within
the given deadline. Specifically, the platform is tested in the cases
of running 2 and 4 models simultaneously. For each case, all models
are allocated an equal number of cores. That is, 2 models are given 2
cores each and 4 models are given 1 core each.

\begin{figure}[h]
  \centering
  \includegraphics[width=.45\textwidth]{figs/perf_vs_modelcnt}
  \caption{Timing impact of co-scheduling multiple DNNs. X-axis shows
    the system configuration: \#of DNN models x \#of CPU cores\/DNN. For
    example, '4x1' means running four DNN models each of which is
    assigned to run on one CPU core, where as '2x2' means running two DNN
    models, each of which is assigned to run on two CPU cores.}
  \label{fig:perf-vs-multimodel}
\end{figure}

@@

@@

The results for the 2 model test are outlined in Figure 3 and Table IV, and the 4 model test is summarized in 
Figure 4 Table V. In the the 2 model test, both of the models showed average inference time increases of around 
5-7 ms, $\sim$10\%, when compared to a baseline of 1 model running on two cores. The difference was even 
greater in the 4 model test, as each model displayed an average inference time increase of 
approximately 15 ms, $\sim$30\%, when compared to a single model running on 1 core.

>>>>

In this experiment, we launch multiple instances of DeepPicar's DNN
model at the same time and measure its impact to their inference
timings.

%% We also test the capability of the DeepPicar to run multiple models at
%% the same time, and whether each model can successfully perform within
%% the given deadline. Specifically, the platform is tested in the cases
%% of running 2 and 4 models simultaneously. For each case, all models
%% are allocated an equal number of cores. That is, 2 models are given 2
%% cores each and 4 models are given 1 core each.

\begin{figure}[h]
  \centering
  \includegraphics[width=.45\textwidth]{figs/perf_vs_modelcnt}
  \caption{Timing impact of co-scheduling multiple DNNs. 1x1: one DNN
    model using one CPU core; 4x1: four DNN models each using one CPU;
    1x2: one DNN model using two CPU cores; 2x2: two DNN models each
    using two CPU cores.} 
  \label{fig:perf-vs-multimodel}
\end{figure}

@@

Figure~\ref{fig:perf-vs-multimodel} shows the results. In the figure,
X-axis shows the system configuration: \#of DNN models x \#of CPU
cores\/DNN. For example, '4x1' means running four DNN models each of
which is assigned to run on one CPU core, whereas '2x2' means running
two DNN models, each of which is assigned to run on two CPU
cores. The Y-axis shows the average inference timing.
Two bars in the left show the impact of co-scheduling four DNN
models. Compared to executing a single DNN model on one CPU core
(1x1), when four DNN models are co-scheduled (4x1), each model
suffers an average inference time increase of approximately 15 ms,
$\sim$24\%. On the other hand, when two DNN models, each using two CPU
cores, are co-scheduled, the average inference timing is increased by
about 7 ms, or 10\%, comapred to the baseline of running one model
using two CPU cores.

%% The results for the 2 model test are outlined in Figure 3 and Table
%% IV, and the 4 model test is summarized in  Figure 4 Table V. In the
%% the 2 model test, both of the models showed average inference time
%% increases of around  5-7 ms, $\sim$10\%, when compared to a baseline
%% of 1 model running on two cores.

@@
